A Motion Blur Resilient Fiducial For Quadcopter Imaging

### 2014-06-09 WACV/paper.tex
Proof read, made footnote in one page.
Looses to loses

\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{color}
\usepackage{url}
\usepackage{comment}
\usepackage{multirow}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\setlength{\floatsep}{7pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{5pt plus 2pt minus 2pt}
\setlength{\intextsep}{5pt plus 2pt minus 2pt}
% Include other packages here, before hyperref.

@@

  fiducials are commonly placed in environments to provide a
  uniquely identifiable object in the scene.  In quadcopter
  applications, these fiducials are often used to evaluate planning
  algorithms given that ground truth positions can be
  detected from the quadcopter's camera.

@@

We also compare our approach with tracking designed for blurred input
scenes.  We have used four image sequences (consisting of around 1000
frames each). Each sequence contains different fiducials so that we
are able to contrast the performance of BLUT~\cite{Wu:2011} with the
proposed method.  From the images in the top rows of
Figure~\ref{fig:BLUT_compare_00} and Figure~\ref{fig:BLUT_compare_01},
we can see that BLUT is able to track the fiducial when the position
of fiducial does not change too much in successive frames. Also, it
can be seen that once BLUT looses track of the fiducial, it is not
able to recover. Since our approach detects the code in each frame,
large changes in the patterns position is not an issue.  Some of our
detection results are also shown in Figure~\ref{fig:BLUT_compare_00}
and Figure~\ref{fig:BLUT_compare_01}.

@@

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output6.jpg}
\end{subfigure}
\caption{\textbf{Top:} Output of BLUT~\cite{Wu:2011}. \textbf{Bottom:}
  Output of our algorithm on the same image 
  sequence. BLUT is able to track the fiducial till the third frame,
  but from the fourth frame onwards, BLUT looses track. In the first
  three frames, the size of the  bounding box is low, but in the fourth
  and fifth frame it is large, indicating a sudden forward movement
  of the quadcopter.} 
\label{fig:BLUT_compare_00}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/15.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output15.jpg}
\end{subfigure}
\caption{{\bf Top:} Output of BLUT~\cite{Wu:2011} on a sequence containing
the ``01'' binary coded fiducial. {\bf Bottom:} Output of our
algorithm on the same image 
sequence. BLUT looses  track from the third frame onwards.}
\label{fig:BLUT_compare_01}
\end{figure*}

\begin{comment}
\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/5.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output5.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``10'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. From the second frame, BLUT looses track.}
\label{fig:BLUT_compare_10}
\end{figure*}

>>>>

\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{color}
\usepackage{url}
\usepackage{comment}
\usepackage{multirow}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\setlength{\floatsep}{7pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{5pt plus 2pt minus 2pt}
\setlength{\intextsep}{5pt plus 2pt minus 2pt}
\interfootnotelinepenalty=10000
% Include other packages here, before hyperref.

@@

Fiducials are commonly placed in environments to provide a
uniquely identifiable object in the scene.  In quadcopter
applications, these fiducials are often used to evaluate planning
algorithms given that ground truth positions can be
detected from the quadcopter's camera.

@@

We also compare our approach with tracking designed for blurred input
scenes.  We have used four image sequences (consisting of around 1000
frames each). Each sequence contains different fiducials so that we
are able to contrast the performance of BLUT~\cite{Wu:2011} with the
proposed method.  From the images in the top rows of
Figure~\ref{fig:BLUT_compare_00} and Figure~\ref{fig:BLUT_compare_01},
we can see that BLUT is able to track the fiducial when the position
of fiducial does not change too much in successive frames. Also, it
can be seen that once BLUT loses track of the fiducial, it is not
able to recover. Since our approach detects the code in each frame,
large changes in the patterns position is not an issue.  Some of our
detection results are also shown in Figure~\ref{fig:BLUT_compare_00}
and Figure~\ref{fig:BLUT_compare_01}.

@@

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output6.jpg}
\end{subfigure}
\caption{\textbf{Top:} Output of BLUT~\cite{Wu:2011}. \textbf{Bottom:}
  Output of our algorithm on the same image 
  sequence. BLUT is able to track the fiducial till the third frame,
  but from the fourth frame onwards, BLUT loses track. In the first
  three frames, the size of the  bounding box is low, but in the fourth
  and fifth frame it is large, indicating a sudden forward movement
  of the quadcopter.} 
\label{fig:BLUT_compare_00}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/15.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output15.jpg}
\end{subfigure}
\caption{{\bf Top:} Output of BLUT~\cite{Wu:2011} on a sequence containing
the ``01'' binary coded fiducial. {\bf Bottom:} Output of our
algorithm on the same image 
sequence. BLUT loses  track from the third frame onwards.}
\label{fig:BLUT_compare_01}
\end{figure*}

\begin{comment}
\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_10/5.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_10/output5.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``10'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. From the second frame, BLUT loses track.}
\label{fig:BLUT_compare_10}
\end{figure*}
